Energy and the CES production function

### 2015-08-06 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change mse to sse.

In contrast, it is not necessarily true that 
CES models will exhibit lower $mse$ than the reference model
shown in Equation~\ref{eq:exponential-only-model}.
The CES model has more fitting parameters,
but it incorporates the factors of production
at constant returns to scale. 
The reference model has $\alpha_1 + \alpha_2 + \alpha_3 = 0$,
whereas the CES model~(Equation~\ref{eq:CESgeneric})
implicitly assumes constant returns to scale.
Thus, if the factors of production~($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
are poorly correlated to output~($y$),
the constant returns to scale constraint may cause higher $mse$ for
the CES model relative to the reference model.

@@

  models <- list()
  for(country in countries){
    for (flavor in flavors){
      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
      fwithE <- formulas[[country]][[flavor]]
      # CD models
      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
      # CES models
      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
                                                                        data = historicalData[[country]], 
                                                                        nest=c(1,2))
      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
      models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
        })
    }      
  }
  # Save models to disk.
  saveRDS(models, file=fileNameCDCES)
}
# Put all exponential model coefficients into a data frame
AllCoeffsExp <- leaf_apply(modelsExp, class = c("lm"), f = function(modExp, id){
  # Parse the id to find details of this model
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = NA,
                    energy = "Without energy", 
                    model = "exp", 
                    nest = NA,
                    cst = "Reject CST"))
  res <- cbind(res, naturalCoef(modExp))
  # Now caluculate mean squared error (mse) for each model.
  sqResids <- resid(modExp)^2
  mse <- sum(sqResids) / (length(sqResids))
  res <- cbind(res, list(mse=mse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)

# Put all the cost-share theorem (CST) model coefficients into a data frame
AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
  # Parse the id to find out whether this is quality-adjusted data, etc.
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
                    model=id_list[[4]], 
                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
                    cst="Adhere to CST"))
  res <- cbind(res, naturalCoef(modCST))
  # Now calculate the mean squared error (mse) for each model.
  sqResids <- resid(modCST)^2
  mse <- sum(sqResids)/(length(sqResids))
  res <- cbind(res, list(mse=mse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)

AllCoeffsNoCST <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
  # Parse the id to find out whether this is quality-adjusted data, etc.
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
                    model=id_list[[4]], 
                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
                    cst="Reject CST"))
  res <- cbind(res, naturalCoef(mod))
  # Now calculate the mean squared error (mse) for each model.
  sqResids <- resid(mod)^2
  mse <- sum(sqResids)/(length(sqResids))
  res <- cbind(res, list(mse=mse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)
AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCST, AllCoeffsNoCST)
# See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
AllCoeffs <- as.data.frame(lapply(AllCoeffs, function(x) unname(unlist(x))))
# Get reference values for lambda and sse.
# ref <- filter(AllCoeffs, cst=="Adhere to CST" & flavor=="Unadjusted" & energy=="Without energy") %>% 
#               select(Country, model, mse, lambda)
ref <- filter(AllCoeffs, model=="exp") %>% select(Country, mse, lambda)
colnames(ref)[colnames(ref)=="mse"] <- "mse_ref"
colnames(ref)[colnames(ref)=="lambda"] <- "lambda_ref"
AllCoeffs <- merge(AllCoeffs, ref)
# Calculate differences relative to the reference model
AllCoeffs <- mutate(AllCoeffs, 
                    Dlambda = abs(lambda) - abs(lambda_ref), 
                    Dmse = mse - mse_ref,
                    percDlambda = Dlambda / abs(lambda_ref) * 100, 
                    percDmse = Dmse / mse_ref * 100)

@@

The mean squared error~($mse$) for any fitted model can be calculated by
%
\begin{equation} \label{eq:mse}
  mse \equiv \frac{1}{N} \sum_{i=1}^N{r_i^2} .
\end{equation}

@@

Table~\ref{tab:CES_sr_gof} shows 
the Solow residual~($\lambda$) and
goodness of fit~($mse$)
for all modeling decisions.
%
<<CES_sr_gof, results="asis">>=
myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
           select(Country, model, flavor, energy, nest, cst, scale, lambda, mse),
         caption="$\\theta$, Solow residual, and $mse$ for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
We can evaluate the effect of modeling decisions on 
goodness of fit and Solow residual by
calculating values relative to the reference model.
To do so, we define 
$\Delta \lambda$ and $\Delta mse$, where
%
\begin{equation} \label{eq:delta_lambda}
  \Delta \lambda \equiv \lambda - \lambda_{ref}
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_mse}
  \Delta mse \equiv mse - mse_{ref},
\end{equation}
%
with~$\lambda_{ref}$ and $mse_{ref}$ being the values 
of the Solow residual and $mse$ for the reference model, respectively.
On a percentage basis,
%
\begin{equation} \label{eq:delta_lambda_perc}
  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_mse_perc}
  \Delta mse \, [\%] = \frac{100 \, \Delta mse}{mse_{ref}} 
            = \frac{100 \, mse}{mse_{ref}} - 1 \; .
\end{equation}

When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta mse$ are negative, 
we observe reduction in the Solow residual ($\lambda$) or
the fitting residuals ($mse$)
relative to the reference model.

Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
$\Delta \lambda \, [\%]$ and $\Delta mse \, [\%]$ 
results for CES models.
%
<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
  scale_size_manual(values=c(2,3.5)) +
  scale_shape_manual(values=c(16,17,18,15)) +
  facet_grid(Country ~ flavor) +
  xlab(expression(paste(Delta * mse, " [%]"))) + 
  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
  ylab(expression(paste(Delta * lambda, " [%]"))) +
  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
  xy_theme() +
  theme(legend.title=element_blank())
@

<<SRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($mse$). $\\lambda$ and $mse$ values for the reference (exponential-only) model are shown as gridlines.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=mse, y=lambda, color=energy, size=cst, shape=nest)) +
  geom_vline(aes(xintercept = mse), filter(AllCoeffs, model=="exp") %>% select(Country, mse), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = lambda), filter(AllCoeffs, model=="exp") %>% select(Country, lambda), colour="gray50", size=0.1) +
  scale_size_manual(values=c(2,4)) +
  scale_shape_manual(values=c(1,0,3,4)) + 
  facet_grid(Country ~ flavor) +
  ylab(expression(lambda)) +
  xy_theme() +
  theme(legend.title=element_blank())
@

@@

@@

Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
on fitted parameters for the Cobb-Douglas model and the exponential-only model.
The Cobb-Douglas models show lower $mse$ than the exponential-only models.
The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
to the exponential-only case.
%
<<Effect_of_CST_CD, results="asis">>=
myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, mse),
         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
and the reference model (exponential-only).
%
<<CD_coeffs, results="asis">>=
myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, mse),
         caption="Model parameters for all Cobb-Douglas models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

Table~\ref{tab:DSRmse_CD} shows $\Delta \lambda$ and $\Delta mse$ results for the Cobb-Douglas models.
%
<<DSRmse_CD, results="asis">>=
myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dmse),
         caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

%
Figures~\ref{fig:DSRmse_CD_graph} and~\ref{fig:percDSRmse_CD_graph} summarize 
$\Delta \lambda$ and $\Delta mse$ 
results for the Cobb-Douglas model.
%
<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst)) +
  facet_grid(Country ~ flavor) +
  scale_size_manual(values=c(2,3.5)) +
  xlab(expression(Delta * mse)) + 
  scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
  ylab(expression(Delta * lambda)) +
  scale_y_continuous(limits=c(-0.04, 0)) +
  xy_theme() + 
  theme(legend.title=element_blank())
@
%
<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst)) +
  facet_grid(Country ~ flavor) +
  scale_size_manual(values=c(2,3.5)) +
  xlab(expression(paste(Delta * mse, " [%]"))) + 
  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
  ylab(expression(paste(Delta * lambda, " [%]"))) +
  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
  xy_theme() + 
  theme(legend.title=element_blank())
@
%
<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
  scale_size_manual(values=c(2,3.5)) +
  scale_shape_manual(values=c(16,17,18,15)) +
  facet_grid(Country ~ flavor) +
  xlab(expression(Delta * mse)) + 
  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
  ylab(expression(Delta * lambda)) +
  xy_theme() +
  theme(legend.title=element_blank())
@
%

>>>>

In contrast, it is not necessarily true that 
CES models will exhibit lower $sse$ than the reference model
shown in Equation~\ref{eq:exponential-only-model}.
The CES model has more fitting parameters,
but it incorporates the factors of production
at constant returns to scale. 
The reference model has $\alpha_1 + \alpha_2 + \alpha_3 = 0$,
whereas the CES model~(Equation~\ref{eq:CESgeneric})
implicitly assumes constant returns to scale.
Thus, if the factors of production~($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
are poorly correlated to output~($y$),
the constant returns to scale constraint may cause higher $sse$ for
the CES model relative to the reference model.

@@

  models <- list()
  for(country in countries){
    for (flavor in flavors){
      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
      fwithE <- formulas[[country]][[flavor]]
      # CD models
      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
      # CES models
      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
                                                                        data = historicalData[[country]], 
                                                                        nest=c(1,2))
      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
      models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
        })
    }      
  }
  # Save models to disk.
  saveRDS(models, file=fileNameCDCES)
}
# Put all exponential model coefficients into a data frame
AllCoeffsExp <- leaf_apply(modelsExp, class = c("lm"), f = function(modExp, id){
  # Parse the id to find details of this model
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = NA,
                    energy = "Without energy", 
                    model = "exp", 
                    nest = NA,
                    cst = "Reject CST"))
  res <- cbind(res, naturalCoef(modExp))
  # Now caluculate mean squared error (sse) for each model.
  sse <- sum(resid(modExp)^2)
  res <- cbind(res, list(sse=sse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)

# Put all the cost-share theorem (CST) model coefficients into a data frame
AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
  # Parse the id to find out whether this is quality-adjusted data, etc.
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
                    model=id_list[[4]], 
                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
                    cst="Adhere to CST"))
  res <- cbind(res, naturalCoef(modCST))
  # Now calculate the mean squared error (sse) for each model.
  sse <- sum(resid(modCST)^2)
  res <- cbind(res, list(sse=sse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)

AllCoeffsNoCST <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
  # Parse the id to find out whether this is quality-adjusted data, etc.
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
                    model=id_list[[4]], 
                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
                    cst="Reject CST"))
  res <- cbind(res, naturalCoef(mod))
  # Now calculate the sum of squared error (sse) for each model.
  sse <- sum(resid(mod)^2)
  res <- cbind(res, list(sse=sse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)
AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCST, AllCoeffsNoCST)
# See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
AllCoeffs <- as.data.frame(lapply(AllCoeffs, function(x) unname(unlist(x))))
# Get reference values for lambda and sse.
ref <- filter(AllCoeffs, model=="exp") %>% select(Country, sse, lambda)
colnames(ref)[colnames(ref)=="sse"] <- "sse_ref"
colnames(ref)[colnames(ref)=="lambda"] <- "lambda_ref"
AllCoeffs <- merge(AllCoeffs, ref)
# Calculate differences relative to the reference model
AllCoeffs <- mutate(AllCoeffs, 
                    Dlambda = abs(lambda) - abs(lambda_ref), 
                    Dsse = sse - sse_ref,
                    percDlambda = Dlambda / abs(lambda_ref) * 100, 
                    percDsse = Dsse / sse_ref * 100)

@@

@@

Table~\ref{tab:CES_sr_gof} shows 
the Solow residual~($\lambda$) and
goodness of fit~($sse$)
for all modeling decisions.
%
<<CES_sr_gof, results="asis">>=
myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
           select(Country, model, flavor, energy, nest, cst, scale, lambda, sse),
         caption="$\\theta$, Solow residual, and $sse$ for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
We can evaluate the effect of modeling decisions on 
goodness of fit and Solow residual by
calculating values relative to the reference model.
To do so, we define 
$\Delta \lambda$ and $\Delta sse$, where
%
\begin{equation} \label{eq:delta_lambda}
  \Delta \lambda \equiv \lambda - \lambda_{ref}
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_sse}
  \Delta sse \equiv sse - sse_{ref},
\end{equation}
%
with~$\lambda_{ref}$ and $sse_{ref}$ being the values 
of the Solow residual and $sse$ for the reference model, respectively.
On a percentage basis,
%
\begin{equation} \label{eq:delta_lambda_perc}
  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_sse_perc}
  \Delta sse \, [\%] = \frac{100 \, \Delta sse}{sse_{ref}} 
            = \frac{100 \, sse}{sse_{ref}} - 1 \; .
\end{equation}

When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta sse$ are negative, 
we observe reduction in the Solow residual ($\lambda$) or
the fitting residuals ($sse$)
relative to the reference model.

Figure~\ref{fig:DSRsse_CES_graph} summarizes 
$\lambda$ and $sse$ 
results for CES models.

<<SRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$). $\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=sse, y=lambda, color=energy, size=cst, shape=nest)) +
  geom_vline(aes(xintercept = sse), filter(AllCoeffs, model=="exp") %>% select(Country, sse), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = lambda), filter(AllCoeffs, model=="exp") %>% select(Country, lambda), colour="gray50", size=0.1) +
  scale_size_manual(values=c(2,4)) +
  scale_shape_manual(values=c(1,0,3,4)) + 
  facet_grid(Country ~ flavor) +
  scale_y_continuous(breaks=c(0, 0.01, 0.02), limits=c(0, 0.03)) +
  xlab("SSE") + 
  ylab(expression(lambda)) +
  xy_theme() +
  theme(legend.title=element_blank())
@

@@

%++++++++++++++++++++++++++++++
\subsection{Resampling} 
\label{sec:resampling}
%++++++++++++++++++++++++++++++

<<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
standardScatterPlot(data=resampleCoeffs, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.1) +
    scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 
    scale_y_continuous(breaks=c(0, 0.005, 0.01), limits=c(0, 0.01)) +
    labs(x=expression(theta), y=expression(lambda))
@

<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
                labels=c("alpha[e]", "alpha[k]", "alpha[l]"))
@

<<resample_graph_sigma1_delta1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)}$ and $\\delta_1$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
standardScatterPlot(data=resampleCoeffs, mapping=aes(delta_1, sigma_1), 
                    facet_formula=~Country, alpha=0.1) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
    labs(x=expression(delta[1]), y=expression(sigma[kl]))
@

<<resample_graph_sigma_delta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)e}$ and $\\delta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
standardScatterPlot(data=resampleCoeffs, mapping=aes(delta, sigma), 
                    facet_formula=~Country, alpha=0.1) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
    labs(x=expression(delta), y=expression(sigma[kle]))
@

@@

Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
on fitted parameters for the Cobb-Douglas model and the exponential-only model.
The Cobb-Douglas models show lower $sse$ than the exponential-only models.
The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
to the exponential-only case.
%
<<Effect_of_CST_CD, results="asis">>=
myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, sse),
         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
and the reference model (exponential-only).
%
<<CD_coeffs, results="asis">>=
myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, sse),
         caption="Model parameters for all Cobb-Douglas models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

Table~\ref{tab:DSRsse_CD} shows $\Delta \lambda$ and $\Delta sse$ results for the Cobb-Douglas models.
%
<<DSRsse_CD, results="asis">>=
myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dsse),
         caption="$\\Delta \\lambda$ and $\\Delta sse$ for Cobb-Douglas models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

%
Figures~\ref{fig:DSRsse_CD_graph} and~\ref{fig:percDSRsse_CD_graph} summarize 
$\Delta \lambda$ and $\Delta sse$ 
results for the Cobb-Douglas model.
%
<<DSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=cst)) +
  facet_grid(Country ~ flavor) +
  scale_size_manual(values=c(2,3.5)) +
  xlab(expression(Delta * sse)) + 
  scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
  ylab(expression(Delta * lambda)) +
  scale_y_continuous(limits=c(-0.04, 0)) +
  xy_theme() + 
  theme(legend.title=element_blank())
@
%
<<percDSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta sse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=cst)) +
  facet_grid(Country ~ flavor) +
  scale_size_manual(values=c(2,3.5)) +
  xlab(expression(paste(Delta * sse, " [%]"))) + 
  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
  ylab(expression(paste(Delta * lambda, " [%]"))) +
  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
  xy_theme() + 
  theme(legend.title=element_blank())
@
%
<<DSRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the CES modles relative to the exponential-only model.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=cst, shape=nest)) +
  scale_size_manual(values=c(2,3.5)) +
  scale_shape_manual(values=c(16,17,18,15)) +
  facet_grid(Country ~ flavor) +
  xlab(expression(Delta * sse)) + 
  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
  ylab(expression(Delta * lambda)) +
  xy_theme() +
  theme(legend.title=element_blank())
@
%
<<percDSRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta sse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
ggplot() +
  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=cst, shape=nest)) +
  scale_size_manual(values=c(2,3.5)) +
  scale_shape_manual(values=c(16,17,18,15)) +
  facet_grid(Country ~ flavor) +
  xlab(expression(paste(Delta * SSE, " [%]"))) + 
  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
  ylab(expression(paste(Delta * lambda, " [%]"))) +
  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
  xy_theme() +
  theme(legend.title=element_blank())
@
